\thetitle

### 2008-06-09 paper.tex
Tweaking rest of paper.

While this work is not inherently specific to wireless networks, since the modeling techniques developed are equally applicable to traffic in wired networks, the results are of special importance to wireless research.
Realistic traffic models have a drastic impact on experimental results in wireless networks~\cite{Karpinski07:realism,Karpinski07:cbr-failure}.
This is primarily because wireless networks are locally resource constrained.
Compare this with the typical situation in wired \caps{LAN}s, where gigabit Ethernet and modern routers  can easily handle all but the most intense levels of traffic.
If a wired network operator expects larger volumes of traffic on a regular basis, the solution is to upgrade the hardware, not to change the network protocols.
In wireless networks, on the other hand, the physical medium cannot be upgraded; protocols must be improved to make better usage of the medium.
Being able to perform experiments with realistic workload is a vital part of the ongoing process of improving wireless protocols.
Without realistic workload models for experiments, performance comparisons may be misleading or even completely wrong~\cite{Karpinski07:cbr-failure}.

@@

% The type, source, and destination nodes of the flow are randomly chosen, using histogram vectors $\vec{t}$, $\vec{s}$, and $\vec{d}$ as the proportional probabilities of each type or node being chosen.\footnote{Since a flow must have distinct source and destination nodes, the sampling of endpoints must be done jointly, avoiding the collisions. The simplest technique is the rejection method: if the same node is chosen for both source and destination, reject that pair and begin the selection process again.}
% Next we use the flow size vector, $\vec{b}$ to randomly sample the number of bytes in the flow. The packet size and inter-packet interval vectors, $\vec{z}$ and $\vec{v}$, allow us to compute the expected average packet size and inter-packet intervals for the flow (see~\Section{flow-totals}), call them $\mean{z}$ and $\mean{v}$. From these, together with the flow size in bytes, we estimate the expected duration of the flow: $\mean{d} = \fracx{b\mean{v}}{\mean{z}}$. We finally choose a start time for the flow, using $\vec{a}$ as a vector of relative probabilities for each bin of start times, but ensuring that the start time plus the expected duration, $\mean{d}$, does not exceed the maximum simulation time for the workflow. From the range of possible values mapping to the chosen start bin, we choose a random time uniformly.
% 
% Having determined the overall parameters of the flow, we generate the actual packets of the flow. The first packet is sent at the chosen start time; the size of each packet is sampled from the histogram of packet sizes, $\vec{z}$; the interval until the next packet is determined from the interval vector, $\vec{v}$. Specifically, an interval index, $k$, is chosen with probability proportional to $\vec{v}(k)$; a second value, $u$, is chosen uniformly from $(0,1]$; the pair $\tuple{k,u}$ is transformed back into a continuous time value using the ``dequantization'' function:
% \begin{align}
% \label{eqn:interval-dequantization}
% \Di(k,u)=v_{\min}+(v_{\max}-v_{\min})\left(\frac{k-u}{d_v}\right)^{\frac{1}{\gamma}}.
% \end{align}
% The packet stream ends when the number of bytes allocated to the flow have been emitted. %The last packet is only the size of the remaining number of bytes.

\section{Expression of Common Properties}
\label{sec:common-properties}

Having defined our representation of network behavior, we turn to deriving useful expressions for commonly used network properties in terms of these algebraic building blocks.

\subsection{Communication Topology}
\label{sec:communication-topology}

@@

\subsection{Expected Average Packet Size \& Intervals}
\label{sec:flow-totals}

From the matrices $\mat{Z}$ and $\mat{V}$, we can compute the expected average packet size, $\mean{z}$, and average inter-packet interval, $\mean{v}$, for each flow. The computations require knowing the values that each matrix column represents. The computed duration is only approximate because information is irrecoverably lost in the quantization process (see \Equation{interval-quantization}). The vectors of representative values for $\mat{Z}$ and $\mat{V}$ are:
\begin{align}
\vec{\sigma}&=\tuple{1,2,3,\dots,d_z},\\
\vec{\tau}&=\tuple{\Di\left(k,\fracx{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
Using these representative values, the expected average packet size and expected average inter-packet interval size for a flow may be computed as
\begin{align}
  \mean{z}&=\frac{\inner{\vec{z}}{\vec{\sigma}}}{\inner{\vec{z}}{\ones{}}}, &
  \mean{v}&=\frac{\inner{\vec{v}}{\vec{\tau}}}{\inner{\vec{v}}{\ones{}}},
\end{align}
respectively, where $\inner{\vec{x}}{\vec{y}}$ denotes the standard inner product of vectors.

\section{Expression of Common Modeling Concepts}
\label{sec:modeling-concepts}

The simplifying assumptions made by most traffic models can be classified into three categories. We use the terms \textit{uniformity}, \textit{marginality}, and \textit{regularity} to describe these classes of assumptions. They are all assumptions about the ``sameness'' of aspects of network behaviors; they differ, however, in whether the make stipulations about uniformity within each flow, across all flows, or within groups of flows. In the following sections, we explore how various modeling concepts can be expressed in the framework of the general matrix model. Models are expressed as transformations that will convert arbitrary traffic matrix instances into similar ones that satisfy the model's assumptions. These transformations will later allow us to evaluate the effect of each model's simplifications on the realism of generated workloads.

\subsection{Uniform Behavior}

@@

Since uniform behaviors entail homogeneity of properties with respect to each flow individually, a trace matrix can be transformed to a matrix satisfying the model's assumptions via right matrix multiplication. Right multiplication mixes the elements within each row, and if the mixing weights are uniform, the result is uniform behavior. For example, to make the roles of the nodes with respect to each flow statistically identical, we transform $\mat{S}$ and $\mat{D}$:
\begin{align*}
\mat{S}' &= \mat{S}\ones{n \times n}/n, & \mat{D}' &= \mat{D}\ones{n \times n}/n.
\end{align*}
This makes all the values in each flow's row identically the average of the original $n$ values. As another example, the constant bit-rate (\caps{CBR}) flow model, in its strictest sense, is an intra-flow model, which stipulates that all the packets in each flow behave identically, having identical sizes and intervals; thus each flow's bit-rate is constant, as the name implies. The strict \caps{CBR} model can be easily expressed with the packets-bytes-duration (\caps{PBD}) model used as an example in \Section{representations}. The pair of matrices $\tuple{\mat{Z},\mat{V}}$ is transformed to \caps{PBD} form using the vectors defined in \Section{flow-totals}: $\tuple{\mat{Z},\mat{V}}\Gamma\in\R^{f \times 3}$, where
\begin{align}
\Gamma=\begin{pmatrix}
\ones{} & \vec{\sigma} & \zeros{} \\
\zeros{} & \zeros{} & \vec{\tau}
\end{pmatrix} \in \R^{(d_v+d_z)\times{3}}.
\end{align}
\Figure{trace-vs-uniform} graphically depicts examples of uniform behaviors as compared to realistic behaviors from traces.
%By replacing $\mat{S}'$ with $\mat{S}$, this can also be viewed as a set of linear constraints on the matrix $\mat{S}$, providing a proscriptive definition

@@

\subsection{Marginal Behavior}

@@

\subsection{Regularized Behavior}

The final form of homogenization we consider, is regularization. This is a restricted form of marginality: we may assume that marginal distributions apply to all the flows in certain groupings. For example, we can provide a distribution of flow sizes on a per-source basis. That is, each source node can have its \textit{own} distribution, and the sizes of its flows are drawn from that distribution, independent of their other properties. This is simply accomplished by left-multiplication by a non-uniform matrix. For example, to make flow behavior uniform on a per source basis, we left-multiply by the ``source-uniformizing'' matrix: $\mat{F}'=(\trans{\mat{SS}}/f)\mat{F}$. Per destination uniformity can be achieved similarly, with left-multiplication by a corresponding destination-uniformizing matrix: $F'=(\trans{\mat{DD}}/f)\mat{F}$.
%Although assumptions about uniformity across flows are common, there is little agreement about which notion of uniformity is most appropriate; often it is simply left unspecified. The confusion arises due to the lack of a unique way of associating flows with nodes. Each node can equally viably be associated with its source or its destination. Which association is more valid? Consider a web request: should the behavior of the request be determined by what the client typically does? Or should the requests that the server typically receives determine behavior? There is no armchair answer: only analysis of real data can give us the answer. The matrix model provides an analytical framework for doing so.
The matrix model has the benefit of making the uniformization of behaviors completely explicit. It also allows us to easily define intermediate choices. If we wish make the behavior of each flow a weighted average of the aggregate behaviors of its source and destination nodes, we can express this easily:
\begin{align}
\mat{F}' = \frac{1}{f}((1-\alpha)(\trans{\mat{SS}})+\alpha(\trans{\mat{DD}}))\mat{F}.
\end{align}
The parameter $\alpha$ allows us to smoothly vary the weighting of the source and destination behaviors. Source-only behavior is given by $\alpha=0$; destination-only by $\alpha=1$; to weight source and destination equally, take $\alpha=\frac{1}{2}$.

@@

%A generic traffic model is a way of generating the six matrices described in \Section{representations}. A trace-derived traffic model transforms the matrices for an actual trace of network behavior into a simplified or regularized form. For experimental comparison, the dimensions of the matrices should all be preserved. If a trace-derived model produces experimental performance metrics that are similar to those produced by the original trace data, then simplifications made by the model are viable; if the performance is distorted, then the simplifications are discarding essential information about the traffic pattern.

@@

%% TODO: differentiate between restrictive versions of models and transformative versions.
%% TODO: distinguish uniform, marginal and regularized models.

@@

\begin{table*}
\begin{center}
\small
\begin{tabular}{|c|c|l|}
\multicolumn{1}{c}{\textbf{model}} &
\multicolumn{1}{c}{\textbf{transformation}} &
\multicolumn{1}{c}{\textbf{description}} \\
\hline
\caps{GMM} & --- & the general matrix model \\\hline\hline
time uniform & $\mat{A}'=\mat{A}(\ones{d_t \times d_t}/d_t)$ & all start times are equally likely \\\hline
node uniform & $\mat{S}'=\mat{S}(\ones{n \times n}/n)$~~~~$\mat{D}'=\mat{D}(\ones{n \times n}/n)$ & nodes behave stochastically identically with respect to flows \\\hline
full uniform & \textit{all uniform transformations} & applies all the uniformity assumptions of the above models \\\hline\hline
time marginal & $\mat{A}'=(\ones{f \times f}/f)\mat{A}$ & start times chosen from marginal distribution of start times \\\hline
size marginal & $\mat{B}'=(\ones{f \times f}/f)\mat{B}$ & flow size (bytes) is chosen independently of other properties \\\hline
node marginal & $\mat{S}'=(\ones{f \times f}/f)\mat{S}$~~~~$\mat{D}'=(\ones{f \times f}/f)\mat{D}$ & nodes behave distinctly, but behavior is independent of flows \\\hline
packet marginal & $\mat{Z}'=(\ones{f \times f}/f)\mat{Z}$~~~~$\mat{V}'=(\ones{f \times f}/f)\mat{V}$ & packet behavior is variable bit-rate, aggregated across all flows \\\hline
full marginal & \textit{all marginal transformations} & applies all the marginality assumptions of the above four models \\\hline\hline
source regular & $\mat{F}'=(\trans{\mat{SS}}/f)\mat{F}$ & flow behaviors are aggregated on a per source-node basis \\\hline
dest regular & $\mat{F}'=(\trans{\mat{DD}}/f)\mat{F}$ & flow behaviors are aggregated on a per destination-node basis \\\hline
mixed regular & $\mat{F}'=\frac{1}{2f}(\trans{\mat{SS}}+\trans{\mat{DD}})\mat{F}$ & flow behaviors are aggregated on a mixed source/destination basis \\\hline
\end{tabular}
\caption{Matrix-based traffic models evaluated by paired differential simulation.}
\label{tab:traffic-models}
\end{center}
\vspace{-2em}
\end{table*}

@@

The remainder of this section proceeds as follows. In \Section{traffic-models} we present the collection of traffic models we will evaluate. In \Section{trace-data} we describe the trace data that serves as the control for our experiments. Our simulation methodology is detailed in \Section{simulations}, and the performance metrics used for statistical comparison of control and test experiments are described in \Section{performance-metrics}. Finally, \Section{measures-of-error} is an in-depth mathematical discussion of the appropriate measure of error for the pairs of metric values that are produced by the paired differential simulation methodology.

@@

After validating the \caps{GMM}, we explore the effects of various uniformity, marginality, and regularization assumptions on the realism of traffic models. The uniform models are the most common, being the simplest both to conceptualize and to implement: simply make no distinction between start times, source or destination nodes. Choose them at random, using no information from reality other than the number of nodes and the possible range of start times. We do not evaluate uniform packet behavior because it has been sufficiently discredited in our previous work.

@@

\begin{figure}[t]
\vspace{0.5em}
\begin{center}
\includegraphics[width=3.3in]{nodes-flows}%
\vspace{-1.25em}%
\caption{The number of active nodes and flows over time.} 
\label{fig:nodes-flows}
\end{center}
\vspace{-2em}
\end{figure}

@@

Finally, we turn to the regularized models. These demonstrate neither exceptionally good nor exceptionally bad behavior. That the regularized models should be similar to the \model{full marginal} model but somewhat more realistic is entirely expected: regularization, the reader will recall, is a restricted form of marginal modeling, where each group of flows has its own marginal distribution. In these cases, the flows are grouped by source node or by destination node. The mixed case uses the average behavior of the other two cases. It is interesting to note that the mixed case is universally worse than either the source or destination case. Clearly, hybridizing the regularization here is not an effective technique. We believe that the cause of this effect is like mixing too many colors yielding an unpleasant shade of brown: any of the colors individually would be better than the nondescript average. As a more general conclusion, arbitrarily mixing model may not always be a good idea, despite the ease with which it is done in the matrix representation of workload behavior.

@@

\section{Discussion}\label{sec:discussion}

@@

%The reader will note that the transformations applied in this paper are all quite simple. Our regularization matrices primarily consisted of ones and zeros. The algebraic representation of complete workload

>>>>

While this work is not inherently specific to wireless networks, since the modeling techniques developed are equally applicable to traffic in wired networks, the results are of special importance to wireless research.
Realistic traffic models have a drastic impact on experimental results in wireless networks~\cite{Karpinski07:realism,Karpinski07:cbr-failure}.
This is primarily because wireless networks are locally resource constrained.
Compare this with the typical situation in wired \caps{LAN}s, where gigabit Ethernet and modern routers  can easily handle all but the most intense levels of traffic.
If a wired network operator expects larger volumes of traffic on a conditional basis, the solution is to upgrade the hardware, not to change the network protocols.
In wireless networks, on the other hand, the physical medium cannot be upgraded; protocols must be improved to make better usage of the medium.
Being able to perform experiments with realistic workload is a vital part of the ongoing process of improving wireless protocols.
Without realistic workload models for experiments, performance comparisons may be misleading or even completely wrong~\cite{Karpinski07:cbr-failure}.

@@

\subsection{Expression of Common Properties}
\label{sec:common-properties}

Having defined our representation of network behavior and presented the procedure for stochastically generating workload, we turn to deriving useful expressions for commonly used network properties in terms of these algebraic building blocks.

\subsubsection{Communication Topology}
\label{sec:communication-topology}

@@

\subsubsection{Expected Average Packet Size \& Intervals}
\label{sec:flow-totals}

From the matrices $\mat{Z}$ and $\mat{V}$, we can compute the expected average packet size, $\mean{z}$, and average inter-packet interval, $\mean{v}$, for each flow.
The computations require knowing the values that each matrix column represents.
The computed duration is approximate because information is irrecoverably lost in the quantization process.
The vectors of representative values for $\mat{Z}$ and $\mat{V}$ are:
\begin{align}
\vec{\sigma}&=\tuple{1,2,3,\dots,d_z},\\
\vec{\tau}&=\tuple{\Di\left(k,\fracx{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
Using these representative values, the expected average packet size and expected average inter-packet interval size for a flow may be computed as
\begin{align}
  \mean{z}&=\frac{\inner{\vec{z}}{\vec{\sigma}}}{\inner{\vec{z}}{\ones{}}}, &
  \mean{v}&=\frac{\inner{\vec{v}}{\vec{\tau}}}{\inner{\vec{v}}{\ones{}}},
\end{align}
respectively, where $\inner{\vec{x}}{\vec{y}}$ denotes the standard inner product of vectors.

\subsection{Expression of Common Modeling Concepts}
\label{sec:modeling-concepts}

The simplifying assumptions made by most traffic models can be classified into three categories. We use the terms \textit{uniformity}, \textit{marginality}, and \textit{conditionality} to describe these classes of assumptions. They are all assumptions about the ``sameness'' of aspects of network behaviors; they differ, however, in whether the make stipulations about uniformity within each flow, across all flows, or within groups of flows. In the following sections, we explore how various modeling concepts can be expressed in the framework of the general matrix model. Models are expressed as transformations that will convert arbitrary traffic matrix instances into similar ones that satisfy the model's assumptions. These transformations will later allow us to evaluate the effect of each model's simplifications on the realism of generated workloads.

\subsubsection{Uniformity}

@@

Since uniform behaviors entail homogeneity of properties with respect to each flow individually, a trace matrix can be transformed to a matrix satisfying the model's assumptions via right matrix multiplication. Right multiplication mixes the elements within each row, and if the mixing weights are uniform, the result is uniform behavior. For example, to make the roles of the nodes with respect to each flow statistically identical, we transform $\mat{S}$ and $\mat{D}$:
\begin{align*}
\mat{S}' &= \mat{S}\ones{n \times n}/n, & \mat{D}' &= \mat{D}\ones{n \times n}/n.
\end{align*}
This makes all the values in each flow's row identically the average of the original $n$ values. As another example, the constant bit-rate (\caps{CBR}) flow model, in its strictest sense, is an intra-flow model, which stipulates that all the packets in each flow behave identically, having identical sizes and intervals; thus each flow's bit-rate is constant, as the name implies. The strict \caps{CBR} model can be easily expressed with the packets-bytes-duration (\caps{PBD}) model used as an example in \Section{representations}. The pair of matrices $[\mat{Z}~\mat{V}]$ is transformed to \caps{PBD} form using the vectors defined in \Section{flow-totals}: $[\mat{Z}~\mat{V}]\,\Gamma\in\R^{f \times 3}$, where
\begin{align}
\Gamma=\begin{pmatrix}
\ones{} & \vec{\sigma} & \zeros{} \\
\zeros{} & \zeros{} & \vec{\tau}
\end{pmatrix} \in \R^{(d_v+d_z)\times{3}}.
\end{align}
\Figure{trace-vs-uniform} graphically depicts examples of uniform behaviors as compared to realistic behaviors from traces.
%By replacing $\mat{S}'$ with $\mat{S}$, this can also be viewed as a set of linear constraints on the matrix $\mat{S}$, providing a proscriptive definition

@@

\subsubsection{Marginality}

@@

\subsection{Conditionality}

The final form of homogenization we consider, is conditionality. This is a restricted form of marginality: we may assume that marginal distributions apply to all the flows in certain groupings. For example, we can provide a distribution of flow sizes on a per-source basis. That is, each source node can have its \textit{own} distribution, and the sizes of its flows are drawn from that distribution, independent of their other properties. This is simply accomplished by left-multiplication by a non-uniform matrix. For example, to make flow behavior uniform on a per source basis, we left-multiply by the ``source-conditioning'' matrix: $\mat{F}'=(\trans{\mat{SS}}/f)\mat{F}$. Per destination uniformity can be achieved similarly, with left-multiplication by a corresponding destination-conditioning matrix: $F'=(\trans{\mat{DD}}/f)\mat{F}$.
%Although assumptions about uniformity across flows are common, there is little agreement about which notion of uniformity is most appropriate; often it is simply left unspecified. The confusion arises due to the lack of a unique way of associating flows with nodes. Each node can equally viably be associated with its source or its destination. Which association is more valid? Consider a web request: should the behavior of the request be determined by what the client typically does? Or should the requests that the server typically receives determine behavior? There is no armchair answer: only analysis of real data can give us the answer. The matrix model provides an analytical framework for doing so.
The matrix model has the benefit of making the conditioning of behaviors completely explicit. It also allows us to easily define intermediate choices. If we wish make the behavior of each flow a weighted average of the aggregate behaviors of its source and destination nodes, we can express this easily:
\begin{align}
\mat{F}' = \frac{1}{f}((1-\alpha)(\trans{\mat{SS}})+\alpha(\trans{\mat{DD}}))\mat{F}.
\end{align}
The parameter $\alpha$ allows us to smoothly vary the weighting of the source and destination behaviors. Source-only behavior is given by $\alpha=0$; destination-only by $\alpha=1$; to weight source and destination equally, take $\alpha=\frac{1}{2}$.

@@

%A generic traffic model is a way of generating the six matrices described in \Section{representations}. A trace-derived traffic model transforms the matrices for an actual trace of network behavior into a simplified or conditionalized form. For experimental comparison, the dimensions of the matrices should all be preserved. If a trace-derived model produces experimental performance metrics that are similar to those produced by the original trace data, then simplifications made by the model are viable; if the performance is distorted, then the simplifications are discarding essential information about the traffic pattern.

@@

%% TODO: differentiate between restrictive versions of models and transformative versions.
%% TODO: distinguish uniform, marginal and conditionalized models.

@@

\begin{table*}
\begin{center}
\small
\begin{tabular}{|c|c|l|}
\multicolumn{1}{c}{\textbf{model}} &
\multicolumn{1}{c}{\textbf{transformation}} &
\multicolumn{1}{c}{\textbf{description}} \\
\hline
\caps{GMM} & --- & the general matrix model \\\hline\hline
time uniform & $\mat{A}'=\mat{A}(\ones{d_t \times d_t}/d_t)$ & all start times are equally likely \\\hline
node uniform & $\mat{S}'=\mat{S}(\ones{n \times n}/n)$~~~~$\mat{D}'=\mat{D}(\ones{n \times n}/n)$ & nodes behave stochastically identically with respect to flows \\\hline
full uniform & \textit{all uniform transformations} & applies all the uniformity assumptions of the above models \\\hline\hline
time marginal & $\mat{A}'=(\ones{f \times f}/f)\mat{A}$ & start times chosen from marginal distribution of start times \\\hline
size marginal & $\mat{B}'=(\ones{f \times f}/f)\mat{B}$ & flow size (bytes) is chosen independently of other properties \\\hline
node marginal & $\mat{S}'=(\ones{f \times f}/f)\mat{S}$~~~~$\mat{D}'=(\ones{f \times f}/f)\mat{D}$ & nodes behave distinctly, but behavior is independent of flows \\\hline
packet marginal & $\mat{Z}'=(\ones{f \times f}/f)\mat{Z}$~~~~$\mat{V}'=(\ones{f \times f}/f)\mat{V}$ & packet behavior is variable bit-rate, aggregated across all flows \\\hline
full marginal & \textit{all marginal transformations} & applies all the marginality assumptions of the above four models \\\hline\hline
source conditional & $\mat{F}'=(\trans{\mat{SS}}/f)\mat{F}$ & flow behaviors are aggregated on a per source-node basis \\\hline
dest conditional & $\mat{F}'=(\trans{\mat{DD}}/f)\mat{F}$ & flow behaviors are aggregated on a per destination-node basis \\\hline
mixed conditional & $\mat{F}'=\frac{1}{2f}(\trans{\mat{SS}}+\trans{\mat{DD}})\mat{F}$ & flow behaviors are aggregated on a mixed source/destination basis \\\hline
\end{tabular}
\caption{Matrix-based traffic models evaluated by paired differential simulation.}
\label{tab:traffic-models}
\end{center}
\vspace{-2em}
\end{table*}

@@

The remainder of this section proceeds as follows. In \Section{traffic-models} we present the collection of traffic models we will evaluate. In \Section{trace-data} we describe the trace data that serves as the control for our experiments. Our simulation methodology is detailed in \Section{simulations}, and the performance metrics used for statistical comparison of control and test experiments are described in \Section{performance-metrics}.
% Finally, \Section{measures-of-error} is an in-depth mathematical discussion of the appropriate measure of error for the pairs of metric values that are produced by the paired differential simulation methodology.

@@

After validating the \caps{GMM}, we explore the effects of various uniformity, marginality, and conditionalization assumptions on the realism of traffic models. The uniform models are the most common, being the simplest both to conceptualize and to implement: simply make no distinction between start times, source or destination nodes. Choose them at random, using no information from reality other than the number of nodes and the possible range of start times. We do not evaluate uniform packet behavior because it has been sufficiently discredited in our previous work.

@@

\begin{figure}[!b]
\begin{center}
\includegraphics[width=3.3in]{nodes-flows}%
\vspace{-1.25em}%
\caption{The number of active nodes and flows over time.} 
\label{fig:nodes-flows}
\end{center}
\vspace{-1.3em}
\end{figure}

@@

Finally, we turn to the conditionalized models. These demonstrate neither exceptionally good nor exceptionally bad behavior. That the conditionalized models should be similar to the \model{full marginal} model but somewhat more realistic is entirely expected: conditionalization, the reader will recall, is a restricted form of marginal modeling, where each group of flows has its own marginal distribution. In these cases, the flows are grouped by source node or by destination node. The mixed case uses the average behavior of the other two cases. It is interesting to note that the mixed case is universally worse than either the source or destination case. Clearly, hybridizing the conditionalization here is not an effective technique. We believe that the cause of this effect is like mixing too many colors yielding an unpleasant shade of brown: any of the colors individually would be better than the nondescript average. As a more general conclusion, arbitrarily mixing model may not always be a good idea, despite the ease with which it is done in the matrix representation of workload behavior.

@@

\section{Discussion}
\label{sec:discussion}

@@

%The reader will note that the transformations applied in this paper are all quite simple. Our conditionalization matrices primarily consisted of ones and zeros. The algebraic representation of complete workload
